\firstname{Christian}
\familyname{Lavoie}
\title{CV}
\address{151 Atwater, CP 72107}{H3J 2Z6, Montr\'{e}al, Canada}
\mobile{+1~(514)~927~7830}
\fax{+1~(514)~931~6159}
\email{clavoie@sandreckoning.com}
\homepage{www.sandreckoning.com}

\begin{document}

\makecvtitle

\begin{langen}
\section{Executive summary}
Flexible professional with unmatched qualifications, able to explore all facets of a technical project. Experienced in programming, systems administration and management of highly-qualified technical teams.
\end{langen}

\begin{langfr}
\section{Sommaire \'{E}xecutif}
Professionel flexible et qualifi\'{e}, capable d'explorer toutes les facettes d'un projet technique et ayant de l'exp\'{e}rience allant de la programmation \`{a} l'administration \`{a} la gestion d'\'{e}quipes extr\^{e}mement qualifi\'{e}es.
\end{langfr}

\begin{langen}
\subsection{Highlights}
\end{langen}
\begin{langfr}
\subsection{Points Saillants}
\end{langfr}

\begin{description}

\begin{langen}
\item[Database administration] Was in charge of one of the largest MySQL (Google's Ads Database and related systems) installations on Earth for nearly 2 years.
\end{langen}
\begin{langfr}
\item[Administration de banques de donn\'{e}es] Ai \'{e}t\'{e} en charge d'une des plus grandes installations MySQL au monde pendant pr\`{e}s de 2 ans.
\end{langfr}

\vspace{2 mm}

\begin{langen}
\item[Team/tech lead] Was elected Tech Lead twice, by different teams of coworkers. First, became one of Google's youngest Tech Leads at 24. Second, most coworkers had a dozen or more years of experience on me.
\end{langen}
\begin{langfr}
\item[Gestion d'\'{e}quipe] Ai \'{e}t\'{e} \'{e}lu chef d'\'{e}quipe par des coll\`{e}gues avec des dizaines d'ann\'{e}es d'exp\'{e}rience chacun(e)s: un des plus jeunes chefs d'\'{e}quipe chez Google \`{a} 24 ans.
\end{langfr}

\vspace{2 mm}

\begin{langen}
\item[Programming] Used to development for clusters of hundreds or thousands of computers, including real-time manipulation of petabytes.
\end{langen}
\begin{langfr}
\item[Programmation] Habitu\'{e} au d\'{e}veloppement sur des syst\`{e}mes de centaines ou milliers d'ordinateurs combin\'{e}s, incluant manipulation de petaoctets en temps r\'{e}el.
\end{langfr}

\end{description}

\begin{langen}
\section{Experience}
\end{langen}
\begin{langfr}
\section{Exp\'{e}rience}
\end{langfr}

\begin{langen}
\cventry{2010--present}{President and owner}{Sand Reckoning Consulting}{Montr\'{e}al, Canada}{}{
\begin{itemize}%
\item Technical due diligence for venture capitalists.
\item Senior technology advisor to startups and entrepreneurs.
\item Point of last resort escalation for emergency production issues.
\end{itemize}}
\end{langen}
\begin{langfr}
\cventry{2010--pr\'{e}sent}{Propri\'{e}taire et pr\'{e}sident}{Sand Reckoning Consulting}{Montr\'{e}al, Canada}{}{
\begin{itemize}%
\item Support pr\'{e}-investissement pour investisseurs en capitaux de risque.
\item Conseil en programmation et administration pour jeunes entreprises en TI.
\item Administration et d\'{e}boggage de syst\`{e}mes complexes en \'{e}tat d'urgences.
\end{itemize}}
\end{langfr}

\vspace{4 mm}

\begin{langen}
\cventry{2011--2012}{Senior programmer and team lead}{Hopper}{Montr\'{e}al, Canada}{}{
\begin{itemize}%
\item In charge of the backend systems team.
\item Debugging and optimization of Cassandra infrastructure.
\end{itemize}}
\end{langen}
\begin{langfr}
\cventry{2011--2012}{Programmeur s\'{e}nior et chef d'\'{e}quipe}{Hopper}{Montr\'{e}al, Canada}{}{
\begin{itemize}%
\item En charge de l'\'{e}quipe des syst\`{e}mes de fond.
\item D\'eboggage et am\'{e}lioration interne de l'infrastructure Cassandra.
\end{itemize}}
\end{langfr}

\vspace{4 mm}

\begin{langen}
\cventry{2010--2011}{Interim CTO}{BlueTrader}{Montr\'{e}al, Canada}{}{In charge of all architectural and technical decisions.}
\end{langen}
\begin{langfr}
\cventry{2010--2011}{CTO Int\'{e}rim}{BlueTrader}{Montr\'{e}al, Canada}{}{En charge de l'architecture informatique et de toutes d\'{e}cisions techniques.}
\end{langfr}

\vspace{4 mm}

\begin{langen}
\cventry{2004--2010}{Senior member of technical staff}{Google}{Mountain View, California}{}{Team Lead (twice); programmer and sysadmin for systems at the biggest scale in the world.}
\begin{itemize}%
\vspace{2 mm}
\item 2009--2010: \textit{Street View} Senior programmer for collection of sensor and photo data, as taken by the worldwide fleet of Street View cars.
\item 2007--2009: \textit{Ads-SRE-DB} Database and systems administrator for one of the largest MySQL databases on the planet. Elected tech lead after less than a year in the team.
\item 2005--2007: \textit{Froogle} et \textit{Google Base} Team lead for a team of 5 junior engineers, in charge of all design, programming and development activities.
\item 2004--2005: \textit{Ads/Deli} Member of a team charged with converting product listings into ads automatically. Programmer.
\end{itemize}
\end{langen}

\begin{langfr}
\cventry{2004--2010}{Membre s\'{e}nior de l`\'{e}quipe technique}{Google}{Mountain View, California}{}{Chef d'\'{e}quipe \`{a} double reprise, programmeur et administrateur de syst\`{e}mes informatiques de taille gigantesque.}
\begin{itemize}%
\vspace{2 mm}
\item 2009--2010: \textit{Street View} Programmeur s\'{e}nior pour la collecte et g\'{e}rance de donn\'{e}es de senseurs et des photos prises par la flotte mondiale de voitures.
\item 2007--2009: \textit{Ads-SRE-DB} Administrateur de syst\`{e}mes s\'{e}nior pour MySQL et divers syst\`{e}mes connexes; pour une des plus grandes installations MySQL au monde. \'{E}lu chef d'\'{e}quipe apr\`{e}s moins d'un an dans l'\'{e}quipe.
\item 2005--2007: \textit{Froogle} et \textit{Google Base} Chef d'\'{e}quipe pour un groupe de 5 d\'{e}veloppeurs et programmeurs juniors. En charge du design, de la programmation et de toutes les activit\'{e}s de d\'{e}veloppement de syst\`{e}mes \`{a} tr\`{e}s grande \'{e}chelle.
\item 2004--2005: \textit{Ads/Deli} Membre d'une \'{e}quipe en charge de la cr\'{e}ation automatique de publicit\'{e}s \`{a} partir de listes d'inventaires.
\end{itemize}
\end{langfr}

\pagebreak

\begin{langen}
\cventry{2001-2004}{Systems Administrator}{McGill University}{Montr\'{e}al, Canada}{}{Sysadmin for a 32-CPUs Beowulf cluster and a variety of UNIX workstations.}
\begin{itemize}%
\item Everyday debugging, administration and production emergency response.
\item \textit{Highlight:} post-mortem extraction of a partially-destroyed hard drive.
\item \textit{Highlight:} debugging of the Linux kernel and the MOSIX environment.
\end{itemize}
\end{langen}
\begin{langfr}
\cventry{2001-2004}{Administrateur de syst\`{e}mes}{Universit\'{e} McGill}{Montr\'{e}al, Canada}{}{Administrateur d'un syst\`{e}me Beowulf \`{a} 32 processeurs et de diverses stations UNIX.}
\begin{itemize}%
\item Administration quotidienne, d\'{e}boggage en \'{e}tat d'urgence, etc.
\item \textit{Point saillant:} extraction post-mortem de donn\'{e}es d'un disque dur partiellement d\'{e}truit.
\item \textit{Point saillant:} d\'{e}boggage du noyau Linux et de l'environnement MOSIX.
\end{itemize}
\end{langfr}

\vspace{4 mm}

\begin{langen}
\cventry{2003}{Teacher Assistant}{McGill University}{Montr\'{e}al, Canada}{}{Assistant to Doina Pr\'{e}cup, for COMP-424: Artificial Intelligence.}
\begin{itemize}%
\item One of the rare undergrad TA's that year.
\item Correcting, tutorials for students, etc.
\end{itemize}
\end{langen}
\begin{langfr}
\cventry{2003}{Auxiliaire d'enseignement}{Universit\'{e} McGill}{Montr\'{e}al, Canada}{}{Assistant de Doina Pr\'{e}cup, pour le cour COMP-424: Intelligence Artificielle.}
\begin{itemize}%
\item Un des rares assistants de professeur \`{a} McGill au niveau du Bac.
\item Corrections, tutoriels pour \'{e}tudiants, etc.
\end{itemize}
\end{langfr}

\vspace{4 mm}

\begin{langen}
\cventry{2001}{Junior programmer}{Meteorological Center of Canada}{Dorval, Canada}{}{Programmer on highly-parallel IRIX systems and vectorial super-computers.}
\begin{itemize}
\item Development of a collaborative Java Applet for meteorological data sharing.
\item Development of a visual interface to control models runnings on super-computers.
\end{itemize}
\end{langen}
\begin{langfr}
\cventry{2001}{Programmeur junior}{Centre de M\'{e}t\'{e}orologie du Canada}{Dorval, Canada}{}{Programmeur sur syst\`{e}mes IRIX et super-ordinateurs vectoriels.}
\begin{itemize}
\item D\'{e}veloppement d'un environemment de collaboration pour m\'{e}t\'{e}orologistes par un applet Java.
\item D\'{e}veloppement d'une interface visuelle pour contr\^{o}ller les mod\`{e}les m\'{e}t\'{e}orologiques sur super-ordinateurs.
\end{itemize}
\end{langfr}

\begin{langen}
\section{Skills}
\end{langen}
\begin{langfr}
\section{Comp\'{e}tences}
\end{langfr}



\begin{minipage}[t]{0.48\maincolumnwidth}

\begin{langen}
\subsection{Programming}
\end{langen}
\begin{langfr}
\subsection{Programmation}
\end{langfr}

\begin{description}
\begin{langen}
\item[Environments] Hadoop, Servlets, Linux and UNIX
\end{langen}
\begin{langfr}
\item[Environnements] Hadoop, Servlets, Linux et UNIX
\end{langfr}

\vspace{2 mm}

\begin{langen}
\item[Languages] C, C++, Haskell, Java
\end{langen}
\begin{langfr}
\item[Langages] C, C++, Haskell, Java
\end{langfr}

\vspace{2 mm}

\begin{langen}
\item[Scripting] Borgmon, JavaScript, Perl, Python, Sawzall
\end{langen}
\begin{langfr}
\item[Scriptage] Borgmon, JavaScript, Perl, Python, Sawzall
\end{langfr}

\end{description}
\end{minipage}
\begin{minipage}[t]{0.04\maincolumnwidth}
\phantom{...}
\end{minipage}
\begin{minipage}[t]{0.48\maincolumnwidth}

\begin{langen}
\subsection{Systems Administration}
\end{langen}
\begin{langfr}
\subsection{Administration de syst\`{e}mes}
\end{langfr}

\begin{description}

\begin{langen}
\item[Databases] Cassandra, HBase, MySQL, PostgreSQL
\end{langen}
\begin{langfr}
\item[Banques de donn\'{e}es] Cassandra, HBase, MySQL, PostgreSQL
\end{langfr}

\vspace{2 mm}

\begin{langen}
\item[Operating Systems] CentOS, Debian, FreeBSD, OpenBSD, RHEL, Ubuntu
\end{langen}
\begin{langfr}
\item[Syst\`{e}mes d'exploitation] CentOS, Debian, FreeBSD, OpenBSD, RHEL, Ubuntu
\end{langfr}

\end{description}

\end{minipage}



\begin{langen}
\section{Activities}
\end{langen}
\begin{langfr}
\section{Activit\'{e}s}
\end{langfr}

\begin{description}

\begin{langen}
\item[Haskellers Montr\'{e}al] Organizer of Montreal's Haskell programmers group.
\item[Perl Mongers Montr\'{e}al] Organizer of Montreal's Perl Mongers programmers group.
\item[Montr\'{e}al Tech Leads] Organizer of the Montreal Startup Tech Leads group (CTOs, Vp Engs, senior developers, etc)
\end{langen}
\begin{langfr}
\item[Haskellers Montr\'{e}al] Organisateur du regroupement de programmeurs Haskell de la grande r\'{e}gion de Montr\'{e}al.
\item[Perl Mongers Montr\'{e}al] Organisateur du regroupement de programmeurs Perl de la grande r\'{e}gion de Montr\'{e}al.
\item[Montr\'{e}al Tech Leads] Organisateur du regroupement de programmeurs s\'{e}niors et chefs techniques d'entreprises de la grande r\'{e}gion de Montr\'{e}al.
\end{langfr}
\end{description}

\begin{langen}
\section{Education}
\end{langen}
\begin{langfr}
\section{\'Education}
\end{langfr}

\begin{langen}
\cventry{2000--2004}{Honours in Computer Science}{McGill University}{Montr\'{e}al, Canada}{\textit{3.49 GPA}}{Honours in Computer Science, Minor in Philosophy}
\end{langen}
\begin{langfr}
\cventry{2000--2004}{Honours in Computer Science}{Universit\'{e} McGill}{Montr\'{e}al, Canada}{\textit{3.49 GPA}}{Majeure en informatique, mineure en philosophie}
\end{langfr}

\begin{langen}
\section{Languages}
\cvlistdoubleitem{\textbf{English}: Excellent, spoken and written}{\textbf{French}: Excellent, spoken and written}
\end{langen}
\begin{langfr}
\section{Langues}
\cvlistdoubleitem{\textbf{Anglais}: Excellent, \'{e}crit et oral}{\textbf{Fran\c{c}ais}: Excellent, \'{e}crit et oral}
\end{langfr}

\end{document}
