%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 2.0 (February 14, 2023)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{letter} % Default font size of the document, can use values of 10pt, 11pt or 12pt, but you may need to adjust margins if reducing font size

%----------------------------------------------------------------------------------------
%	FONTS
%----------------------------------------------------------------------------------------

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{fouriernc} % Use the URW Schoolbook L font, similar to New Century Schoolbook

%----------------------------------------------------------------------------------------
%	MARGINS
%----------------------------------------------------------------------------------------

\usepackage{geometry} % Required for adjusting page dimensions and margins

\geometry{
	paper=a4paper, % Paper size, change to letterpaper for US letter size
	top=2cm, % Top margin
	bottom=2.5cm, % Bottom margin
	left=3.25cm, % Left margin
	right=3.25cm, % Right margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE
%----------------------------------------------------------------------------------------

\date{\raggedleft\today} % Left-aligned date of the letter, use \today for the current date

\begin{letter}{}

\vspace{1cm} % Vertical whitespace

\opening{CEO Sheila Stafford,}

I am writing to you with respect to the currently opened position of VP of Engineering at TeamSense, as shared with me by Jemery Wadsack.

Having been a freelancer myself earlier in my career I am intimately familiar with the ups and downs of hourly employees; and having managed the same I am all too aware of the limitations of all too many of the current practices around the administration thereof. That is why I fast became interested in the position when it was announced by Mr. Wadsack.

In my career so far I have had the pleasure of twice being in a very similar position, once bringing a 50+ strong team of developers, systems administrators and quality analysts from bottom-of-the-barrel team morale and high turnover to, during my tenure, the only team with no turnover whatsoever; another time growing a single team of 6 developers (with exactly 0 women) to 4 teams totally 20+ developers and analysts including almost 20\% women representation in less than one year.

I would love to have a call to discuss all of this with you as soon as is convenient for the both of us. I can be reached at 514-927-7830 or at the videoconferencing service of your choice. Thanks for taking the time to read this short letter and considering my application.

Sincerely, \\
Christian Lavoie

% \encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this line for no enclosures

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
